Digging Deeper Into the State of the Practice for Domain Specific Research Software

### 2022-02-18 StateOfPractice/Papers/ICCS-2022-SOP_MethodologyPlusExamples/DigDeep.tex
Revisions to Section 6: Comparison of Processes to Other Research Software

The interview data on development processes is used to answer research question
\rqref{RQ_CompareMethodologies}.  This data should be contrasted with the
development process used by research software in general. The literature
suggests that scientific developers naturally use an agile philosophy
\cite{CarverEtAl2007,Segal2005}, or an amethododical process \cite{Kelly2013}.
Another point of comparison should be on the use of peer review, since peer
review is frequently recommended in software development
guidelines~\cite{HerouxEtAl2008,OrvizEtAl2017,USGS2019}.

The LBM example confirms an informal, agile-like, process.
The development process is not explicitly indicated in the artifacts
for most of the packages. However, during interviews one developer (ESPResSo)
told us their non-rigorous development model is like a combination of agile and
waterfall. Employing a loosely defined process makes sense for LBM software,
given that the teams are generally small and self-contained. One of the
developers (ESPResSo) that was interviewed also noted that an ad hoc peer review
process is used.

>>>>

The interview data on development processes is used to answer research question
\rqref{RQ_CompareMethodologies}.  This data should be contrasted with the
development process used by research software in general. The literature
suggests that scientific developers naturally use an agile philosophy
\cite{CarverEtAl2007,Segal2005}, or an amethododical process \cite{Kelly2013}.
Another point of comparison should be on the use of peer review, since peer
review is frequently recommended~\cite{HerouxEtAl2008,OrvizEtAl2017,USGS2019}.

The LBM example confirms an informal, agile-like, process. The development
process is not explicitly indicated in the artifacts. However, during interviews
one developer (ESPResSo) told us their non-rigorous development model is like a
combination of agile and waterfall. Employing a loosely defined process makes
sense for LBM software, given that the teams are generally small and
self-contained. One of the developers (ESPResSo) also noted that they use an ad
hoc peer review process.
